Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-24 paper/ijcai/paper.tex
paper

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	  \begin{tabular}{lccc}
		\toprule
		Project            & \# top-5 & \# top-10  & \% $\Delta$  \\ 
		\midrule
		\lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		\cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		\closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.61 \%  & 92.31 \% & 7.70 \%      \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%       \\   %\comments{& 76    &  -}\\
		\mockito{}         & 63.16 \%  & 71.05 \% & 7.89 \%    \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fsws}
\end{table}

@@

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{llllll}
		\toprule
		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\ 
		\midrule
		\chart{}  & 6 & 23.1\% & 4 & 15.4 \%  & 26\\
		\jtime{}  &  &  &  &   & \\
		\bottomrule
	\end{tabular}
	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
	\label{tab:fs}
\end{table*}
\normalsize

@@

\subsubsection{RQ2: \textit{How effective is the \comb{} combination for bug localization?}}

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$             &  \comb{}-5  & \comb{}-10 \\ 
		\midrule
		$<0$  & 5 & 4 \\ 
		$=0$  & 6 & 7 \\ 
		$>0$  & 15 & 15 \\

@@

\subsection{Reduction Performance of \ds{}}

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		Project             &  top-5  & top-10 \\ 
		\midrule
		\chart{}  & 59.30\% & 53.64\% \\ 		
		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
	\label{tab:red}
\end{table}
\normalsize

>>>>

\subsection{Dynamic Slicing}

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  top-5  & top-10 \\ 
		\midrule

        \lang{}            &  & \\ 	
        \cmath{}           &  & \\
        \closure{}          &  & \\	
		\chart{}			& 59.30\% & 53.64\% \\ 	
        \jtime{}            &  & \\	
        \mockito{}          &  & \\

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
	\label{tab:red}
\end{table}
\normalsize

@@

\begin{table*}[h]
	\centering
	  \begin{tabular}{|l|ccc|cccc|c|}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{SFL+DS-$k$} & \multirow{2}{*}{\# Faults} \\

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
		\midrule
		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.62\% & 26    \\  %\comments{& 92    &  -}\\
		% \jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%       \\   %\comments{& 76    &  -}\\
		% \mockito{}         & 63.16 \%  & 71.05 \% & 7.89 \%    \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fsws}
\end{table*}

@@

% \begin{table*}[h]
% 	\centering
% 	\setlength{\tabcolsep}{4pt}
% 	\begin{tabular}{llllll}
% 		\toprule
% 		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\
% 		\midrule
% 		\chart{}  & 20 & 76.92\% & 22 & 84.62\%  & 26\\
% 		\jtime{}  &  &  &  &   & \\
% 		\bottomrule
% 	\end{tabular}
% 	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
% 	\label{tab:fs}
% \end{table*}
% \normalsize

@@

\subsubsection{RQ3: \textit{How effective is the \comb{} combination for bug localization?}}

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
		\midrule
		$<0$  & 19.2\% & 15.4\% \\ 
		$=0$  & 23.1\% & 26.9\% \\ 
		$>0$  & 57.7\% & 57.7\% \\

@@
